Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-05 prop_iop.tex
prop_iop.tex \subsection{From Interval-valued to Real-valued} Updating..

\begin{lemma}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}

@@

\begin{definition}\label{def:delta-deterministic}An interval-valued
probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\delta$-deterministic if either $\left[l,r\right]\subseteq\left[0,\delta\right]$
or $\left[l,r\right]\subseteq\left[1-\delta,1\right]$ for every $\left[l,r\right]\in\mathscr{I}$.\end{definition}

Recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $0$-deterministic.
For another example, given a three-dimensional Hilbert space, $\iota_{\frac{1}{3}}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} $
is a $\frac{1}{3}$-deterministic. However, we will prove there is
no $\delta$-deterministic probability measures for small $\delta$
due to the Kochen-Specker theorem.

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\delta$-deterministic probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
with $\delta<\frac{1}{3}$, then $\mu:\events\rightarrow\left[0,1\right]$
defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)\subseteq\left[0,\delta\right]$ ;\\ 
1 & if $\bar{\mu}(P)\subseteq\left[1-\delta,1\right]$
}\end{equation}
is a cryptodeterministic measure.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=0\Rightarrow\bar{\mu}(P)\subseteq\left[0,\delta\right]\\
\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
Similarly, when $\pmeas\left(P\right)=1$, we also have $\pmeas\left(\mathbb{1}-P\right)=1-\pmeas\left(P\right)$.
\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, we
have $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})$.
Without loss of generality, there are two cases:
\begin{itemize}
\item If $\pmeas\left(P_{0}\right)=\pmeas\left(P_{1}\right)=0$, then
\begin{equation}\eqalign{ 
& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[0,2\delta\right]\\
\overset{2\delta<1-\delta}{\Rightarrow} & \bar{\mu}\left(P_{0}+P_{1}\right)\cap\left[1-\delta,1\right]=\emptyset\Rightarrow\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[0,\delta\right]\\
\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=0=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
}\end{equation}
\item If $\pmeas\left(P_{0}\right)=0$ and $\pmeas\left(P_{1}\right)=1$,
then
\begin{equation}\eqalign{ 
& \bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[1-\delta,1\right]\\
\Rightarrow & \pmeas\left(P_{0}+P_{1}\right)=1=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
}\end{equation}
\end{itemize}
Therefore, we always have $\pmeas\left(P_{0}+P_{1}\right)=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)$.
By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\delta$-deterministic
probability measure for $\delta<\frac{1}{3}$.\end{cor}

>>>>

\begin{lemma}\label{lemma:real2interval}Consider a regular pair~$\left(\mathscr{I},\iota\right)$.
Then, given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
a function~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$ is a quantum IVPM.\end{lemma}

@@

\begin{definition}\label{def:delta-deterministic}An interval-valued
probability measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
is called $\left(1/n,\delta\right)$-deterministic if for every $\left[l,r\right]\in\mathscr{I}$,
there is a $k\in\mathbb{Z}$ such that $\left[l,r\right]\subseteq\left[k/n-\delta,k/n+\delta\right]$.\end{definition}

Recall $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
so that a $\mathscr{I}_{\mathrm{D}}$-valued QIVPM is $\left(1,0\right)$-deterministic.
For another example, given a three-dimensional Hilbert space, 
\begin{equation}
\iota_{\infty}\circ\mu_{\frac{\mathbb{1}}{3}}^{\mathrm{B}}:\events\rightarrow\left\{ \imposs,\left[\frac{1}{3},\frac{1}{3}\right],\left[\frac{2}{3},\frac{2}{3}\right],\necess\right\} 
\end{equation}
is a $\left(1,\frac{1}{3}\right)$-deterministic and $\left(\frac{1}{3},0\right)$-deterministic.
However, we will prove there is generally no $\left(1/n,\delta\right)$-deterministic
probability measures when $\delta$ is much smaller than $1/n$.

\begin{lemma}\label{lemma:QIVPM2QCM}Given a Hilbert space of dimension\nb$d$,
and a quantum $\left(1/n,\delta\right)$-deterministic probability
measure\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ with $\delta<1/\left(3n\right)$,
if $\bar{\mu}(P)\subseteq\left[k/n-\delta,k/n+\delta\right]$, let
$\mu(P)=k/n$, then $\mu:\events\rightarrow\left[0,1\right]$ is a
quantum IVPM. In another word, $\iota_{\infty}\circ\mu$ is $\left(1/n,0\right)$-deterministic
by lemma~\ref{lemma:real2interval}.\end{lemma}

\begin{proof}~
\begin{itemize}
\item Since $\bar{\mu}(\mathbb{0})=\imposs$, we have $\mu(\mathbb{0})=0$.
\item Since $\bar{\mu}(\mathbb{1})=\necess$, we have $\mu(\mathbb{1})=1$.
\item For every event $P$, we have 
\begin{equation}\eqalign{ 
& \pmeas\left(P\right)=\frac{k}{n}\Rightarrow\bar{\mu}(P)\subseteq\left[\frac{k}{n}-\delta,\frac{k}{n}+\delta\right]\\
\Rightarrow & \bar{\mu}(\mathbb{1}-P)=\left[1,1\right]-\bar{\mu}(P)\subseteq\left[1-\frac{k}{n}-\delta,1-\frac{k}{n}+\delta\right]\\
\Rightarrow & \pmeas\left(\mathbb{1}-P\right)=1-\frac{k}{n}=1-\pmeas\left(P\right)\textrm{ .}
}\end{equation}
\item Given a pair of orthogonal operators\nb$P_{0}$ and $P_{1}$, let
$\pmeas\left(P_{0}\right)=k_{0}/n$ and $\pmeas\left(P_{1}\right)=k_{1}/n$.
Then, 
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}(P_{0})+\bar{\mu}(P_{1})\subseteq\left[\frac{k_{0}+k_{1}}{n}-2\delta,\frac{k_{0}+k_{1}}{n}+2\delta\right]\textrm{ .}
\end{equation}
Since $\delta<1/\left(3n\right)$, we have
\begin{equation}
\frac{k_{0}+k_{1}-1}{n}+\delta<\frac{k_{0}+k_{1}}{n}-2\delta\le\frac{k_{0}+k_{1}}{n}+2\delta<\frac{k_{0}+k_{1}+1}{n}-\delta\textrm{ .}
\end{equation}
The previous inequality implies that if$\bar{\mu}\left(P_{0}+P_{1}\right)$
overlap with any interval of the form $\left[k/n-\delta,k/n+\delta\right]$
for some $k$, $k$ must be $k_{0}+k_{1}$, i.e., 
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\left[\frac{k_{0}+k_{1}}{n}-\delta,\frac{k_{0}+k_{1}}{n}+\delta\right]\textrm{ .}
\end{equation}
Therefore, 
\begin{equation}
\pmeas\left(P_{0}+P_{1}\right)=\frac{k_{0}+k_{1}}{n}=\pmeas\left(P_{0}\right)+\pmeas\left(P_{1}\right)\textrm{ .}
\end{equation}
By induction, we have $\pmeas\left(\bigcup_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\pmeas(P_{i})$
for any mutually orthogonal events\nb$\left\{ P_{i}\right\} _{i=1}^{N}$. 
\end{itemize}
\end{proof}

@@

\begin{cor}\label{cor:Kochen-Specker-IVPM}Given a Hilbert space
of dimension\nb$d\ge3$, there is no quantum $\left(1,\delta\right)$-deterministic
probability measure for $\delta<\frac{1}{3}$.\end{cor}

In general~\cite{Redhead1987-REDINA}, Gleason's theorem asserts
that a quantum probability measure must be continuous. Therefore,
a $\left(1/n,0\right)$-deterministic QIVPM exists if and only if
$d\mid n$, and so does a $\left(1/n,\delta\right)$-deterministic
QIVPM for $\delta<1/\left(3n\right)$.
